Building a Frankenstien Classification Model for Multiple Complaint Labels

### 2019-05-10 Code/dallin_annotations/11_build_multi_classifier.Rmd
Added a description to the dataset used (which was drawn from the 07 file).

## Load the Training Dataset
This dataset was created in file 07_build_classifier.Rmd
```{r}
load(here::here("Output", "train_data.dat"))
```

>>>>

## Load the Training Dataset
This dataset was created in file 07_build_classifier.Rmd. This dataset contains tweets that have been processed by unsupervised models (a fastText word embeddings model, and a PCR model trained on the fastText word embeddings). These unsupervised models were trained on millions of tweets instead of a few thousand, so we expect them to perform well on phrases and words that were not included in the relatively small labeled training dataset of a few thousand tweets.
```{r}
load(here::here("Output", "train_data.dat"))
```
